\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{tikz}
\usepackage{background}
\usepackage{fontspec}
\usetikzlibrary{calc}

\backgroundsetup{angle = 0, scale = 1, vshift = -2ex,
  contents = {\tikz[overlay, remember picture]
    \draw[line width = 2.5pt, color = black!100]
           ($(current page.north west)+(1cm,-1cm)$)
           rectangle ($(current page.south east)+(-1,1)$);}}


\geometry{top=0.5in, bottom=0.5in, left=0.5in, right=0.5in}
\pagestyle{empty}
\fancyhf{}

\onehalfspacing
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}
\title{\textbf{Project Proposal: [Your Project Title]}}
\author{Your Name \\ Your Institution \\ Your Email}
\date{\today}

\begin{document}
% University name
\begin{center}

    {\Large \textbf{Vemana Institute of Technology} \\[0.2em]}
    \textbf{Affiliated to Visvesvaraya Technological University, Belagavi}\\[0.2em]{Bengaluru - 560034}\\[3em]

    {\fontsize{20}{0}\selectfont\textbf{PROJECT PROPOSAL}} \\[1em]
    {\fontsize{15}{0}\selectfont\textbf{BLOCKCHAIN BASED DATA INTEGRITY SYSTEM}} \\[3em]
    
    {\fontsize{12}{0}\textbf{SYNOPSIS}} \\[0.5em]
    \begin{quote}
      \small
      In today's digital world, everything from phone bills to diplomas is available online and we need mechanisms in place to authenticate these digital documents. 
      Employers and academic institutions often face challenges in verifying credentials due to the risk of falsified certificates. 
      Current methods rely on centralized databases, which are susceptible to tampering, data leaks, and attacks from hackers. 
      There is a pressing need for a decentralized and tamper-proof system to securely store and verify academic records.\newline \newline
      The objective of this project is to design and develop a blockchain-based system that allows universities to store academic records; mainly digital diplomas — securely.
      Employers and authorized university officials will be able to verify the authenticity of these records via the blockchain. 
      This ensures the integrity and immutability of academic credentials, reducing the risk of fraud and adding ease of verification for employers. \newline \newline
      By the end of the project, we expect to have a fully functional blockchain-based system for academic record storage and verification. 
      The system will provide a secure, decentralized way to store and validate academic records, ensuring that the records are tamper-proof and easily verifiable by authorized parties.
    \end{quote}

    % Use minipage to keep content within the borders
    \vfill
    \begin{minipage}[b]{0.45\textwidth}
      \begin{center}
        {\fontsize{20}{0}\textbf{Batch Number 15}} \\[0.5em]
        \textbf{5th Semester - CSE 'B'}\\[0.5em]
        \textbf{Muhammed Abdul Muid - } \textbf{1VI22CS064}\\[0.5em]
        \textbf{Rohan Reddy - } \textbf{1VI22CS097}\\[0.5em]
        \textbf{Santhosh Kumar S - } \textbf{1VI22CS106}\\[0.5em]
        \textbf{Vishwas S - } \textbf{1VI22CS125}\\[3em]
      \end{center}
    \end{minipage}
    
    \vfill
    \begin{minipage}[b]{0.45\textwidth}
      \begin{center}        
        {\fontsize{20}{0}\textbf{Project Guide}} \\[0.5em]
        \textbf{Prof. Menaka A} \\[2em]
        \textbf{------------------} \\[0.5em]
      \end{center}
    \end{minipage}

\end{center}

% Your content goes here
\end{document}
